Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Populations.

### 2023-09-22 src/sections/fidanka.tex
Began final clean up before sending to co authors

\fidanka uses MIST formatted isochrones \citep{Dotter2016} as input along
with distance modulus, B-V color excess, binary mass fraction, and bolometric
corrections. An arbitrarily large number of isochrones may be used to define an
arbitrary number of populations. Synthetic stars are samples from each
isochrone based on a definable probability (for example it is believed that
$\sim90\%$ of stars in globular clusters are younger population
{\color{red}[CITATION]}). Based on the metallicity, $\mu$, and E(B-V) of each
isochrone, bolometric corrections are taken from bolometric correction tables.
Where bolometric correction tables do not include exact metallicities or
extinctions a linear interpolation is preformed between the two bounding
values. {\color{red}[FIGURE]} shows an example of a synthetic CMD generated
from a set of 2 NGC 2808 isochrones as well as a comparison between those
isochrones and the measured fiducial line of the synthetic population.

>>>>

\fidanka uses MIST formatted isochrones \citep{Dotter2016} as input along
with distance modulus, B-V color excess, binary mass fraction, and bolometric
corrections. An arbitrarily large number of isochrones may be used to define an
arbitrary number of populations. Synthetic stars are samples from each
isochrone based on a definable probability (for example it is believed that
$\sim90\%$ of stars in globular clusters are younger population
\citep[e.g.][]{Suntzeff1996, Carretta2013}). Based on the metallicity, $\mu$, and E(B-V) of each
isochrone, bolometric corrections are taken from bolometric correction tables.
Where bolometric correction tables do not include exact metallicities or
extinctions a linear interpolation is preformed between the two bounding
values.

### 2023-09-22 src/sections/fitting.tex
Began final clean up before sending to co authors

\subsection{The Number of Populartions in NGC 2808}
\fidanka provides a somewhat straigtforward way to estimate the number of populations expected in a given magnitude bin given the observations. See Section \ref{sec:fidanka} for specific implimentaiton details. Here we preform an analysis of the number of populations seen in the NGC 2808 F814W-F274W vs F814W color-magnitude diagram. We find that for the majority of the main sequence and red giant branches BGMM prefers two populations; wherease, near the main sequnce turn off and on the majority of the subgiant branches BGMM prefers a single population model.

{\color{red} Make Figure showing the BGMM fit predictions for each star vs. distance to pop mean line, does a good job of visualizing the predicted number of populations}

>>>>

\subsection{The Number of Populartions in NGC 2808}
In order to estimate the number of populations which ideally fit the NGC 2808
F275W-F814W photometry without overfitting the data we make use of silhouette
analysis \citep[][and in a similar manner to how \citet{Valle2022}
preform their analysis of spectroscopic data]{ROUSSEEUW198753}. We find the average silhouette score for all tagged
clusters identified using BGMM in all magnitude bins over the CMD using the
standar python module \texttt{sklearn}. Figure \ref{fig:clusterAn} shows the
silhouette analysis results and that 2 populations fit the photometry most
ideally. This is in line with what our BGMM model predicts for the majority of
the the CMD.

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{src/figures/ClusterAnalysis.pdf}
  \caption{Silhouette analysis for NGC 2808 F275W-F814W photometry. The Silhouette scores
  are an average of score for each magnitude bin. Positive scores incidate that the clustering
  algorithm produced well distinguised clusters while negative scores indicate clusters which are not
  well distinguised.}
  \label{fig:clusterAn}
\end{figure}
